Postural changes mediate children's visual access to social information

### 2018-01-13 writeup-cogsci-copy/cogsci2018.Rmd
All detectors in ggplot2 facets

```{r echo=FALSE, include=FALSE}
d <- read_csv("../data/consolidateddata/consolidated_data_3dets.csv") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

## make long form version for plotting both face detections on same graph
dlong <- d %>%
  mutate(id = paste(subid,frame)) %>%
  gather(key = detectorType, value = face, faceMT, faceOP) %>%
  mutate(detectorType=as.factor(detectorType))

# for better plotting names
levels(detectorType) <- c("MTCNN", "OpenPose") 
```

@@

```{r fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=6, fig.height=3, fig.cap = "R plot" }

@@

# Changes in Access to Faces
```{r fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=2, fig.cap = "Proportion face (left) and hand (right) detections as a function of participant's age. Note that the axes are different; hands were detected overall much less frequently in this dataset." }
facebyAge <- dlong %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test, detectorType) %>%
  summarise(face = mean(face)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

handsbyAge <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(hands = mean(handOP)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

p1<-ggplot(facebyAge, aes(x = age.at.test, y = face, color = detectorType, size = len)) +
    geom_jitter(width = .25) + 
    geom_smooth() +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(1,4),name = "Video Length (mins)") + 
    ylab("Proportion Face Detections") + 
    xlab("Age (months)") + 
    theme_bw() +
    theme(legend.position="bottom", legend.box = "horizontal")

p2<-ggplot(handsbyAge, aes(x = age.at.test, y = hands, size = len)) +
    geom_jitter(width = .25) + 
    geom_smooth() +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(1,4),name = "Video Length (mins)") + 
    ylab("Proportion Hand Detections") + 
    xlab("Age (months)") + 
    theme_bw() +
    theme(legend.position="bottom", legend.box = "horizontal")

@@

```{r faceByPostureFig, fig.env="figure*", fig.pos = "h", fig.align = "center", num.cols.cap=2, fig.width=6, fig.height=2, fig.cap = "Proportion of face detections as a function of infant's posture, using the MTCNN3 detections (left panel) and OpenPose detections (right panel)"}

facebyPosture <- dlong %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid,detectorType) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

handbyPosture <- d %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(hand = mean(handOP)) %>%
  group_by(age.grp)

p2=ggplot(handbyPosture, aes(x = factor(age.grp), y = hand, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion Hand Detections") + 
  xlab("Age (months)") + 
  ggtitle("Hand detections") +
  theme_bw()

p1=ggplot(facebyPosture, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion Face Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw() +
  theme(strip.background = element_blank(), strip.text.y = element_blank())

grid.arrange(p1,p2,nrow = 1, widths=2:1)

```{r faceByOrientFig, fig.env="figure*", fig.pos = "h", fig.align = "center", num.cols.cap=2, fig.width=6, fig.height=2, fig.cap = "Proportion of face detections as a function of caregiver's orientation,using the MTCNN3 detections (left panel) and OpenPose detections (right panel)" }
faceByOrientation <- dlong %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid, detectorType) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

ggplot(faceByOrientation, aes(x = factor(age.grp), y = face, col = orientation)) + 
  geom_boxplot() + 
  ylab("Proportion Face Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw() 
  # theme(legend.position="bottom", legend.box = "horizontal")

@@

# Changes in Access to Hands

Next, we examined whether we would see similar trends in infant and children's access to hands.

>>>>

```{r echo=FALSE, include=FALSE}
d <- read_csv("../data/consolidateddata/consolidated_data_4dets.csv") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

## make long form version for plotting both face detections on same graph
dlong <- d %>%
  mutate(id = paste(subid,frame)) %>%
  gather(key = detectorType, value = detection, faceMT, faceOP, handOP, wristOP) %>%
  mutate(detectorType=as.factor(detectorType))

# for better plotting names
#levels(dlong$detectorType) 
#[1] "faceMT"  "faceOP"  "handOP"  "wristOP"
levels(dlong$detectorType) <- c("MTCNN-Faces", "OpenPose-Faces","OpenPose-Hands", "OpenPose-Wrists") 
```

@@

```{r fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion time that infants in each age group spent in each posture (left panel) and orientation relative to their caregiver (right  panel)." }

@@

# Changes in Access to Faces
```{r fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion face (left) and hand (right) detections as a function of participant's age. Note that the axes are different; hands were detected overall much less frequently in this dataset." }
detectionsByAge <- dlong %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test, detectorType) %>%
  summarise(detections = mean(detection)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth() +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.2,2),name = "Video Length (mins)") +
    ylab("Proportion Detections") +
    xlab("Age (months)") +
    scale_color_manual(values=c("#1F618D", "#7FB3D5", "#C70039", "#FF5733")) +
    facet_grid(~detectorType, scales = "free") +
    theme_bw()
```

```{r faceByPostureFig, fig.env="figure*", fig.pos = "h", fig.align = "center", num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Proportion of face detections as a function of infant's posture, using the MTCNN3 face detections and OpenPose face detections (left two panels) and the proportion of hand detections as a function of infant's posture, using OpenPose hand detections and the OpenPose wrist detections. "}

detectionsByPosture <- dlong %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid,detectorType) %>%
  summarise(face = mean(detection)) %>%
  group_by(age.grp)

ggplot(detectionsByPosture, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion  Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw()

@@

```{r faceByOrientFig, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, num.cols.cap=2, fig.cap = "Proportion of face detections as a function of caregiver's orientation,using the MTCNN3 detections (left panel) and OpenPose detections (right panel)" }
detectionsByPosture <- dlong %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid,detectorType) %>%
  summarise(detections = mean(detection)) %>%
  group_by(age.grp)

ggplot(detectionsByPosture, aes(x = factor(age.grp), y = detections, col = orientation)) + 
  geom_boxplot() + 
  ylab("Proportion  Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw() 
```

@@
